cardinalR: Generating interesting high-dimensional data structures

### 2025-09-19 paper-cardinalR.Rmd
Updated pyramid section and added fixed radius value

An S-curve structure (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:scurve)"} else { "Figure \\@ref(fig:scurve-proj)"})`) simulates data that lies along a smooth, non-linear manifold. The functions generate both the standard S-curve shape and, similar to the cube generator, an S-curve variant with structured hole that introduce missing or incomplete region. These variations are useful for evaluating how well algorithms capture non-linear geometry and handle incomplete manifolds in high-dimensional data. Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:scurve-tb-html)', '\\@ref(tab:scurve-tb-pdf)'))` summarizes these functions.

@@

To introduce missing or incomplete regions on the manifold, `gen_scurvehole(n, p)` (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:scurve) b"} else { "Figure \\@ref(fig:scurve-proj) b"})`) removes a subset of points near a designated anchor, creating a hole in the S-curve. This produces a hollowed manifold while preserving the overall curvature and structure of the S-curve.

>>>>

An S-curve structure (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:scurve)"} else { "Figure \\@ref(fig:scurve-proj)"})`) simulates data that lies along a smooth, non-linear manifold. The functions generate both the standard S-curve shape and, a S-curve variant with structured hole that introduce missing or incomplete region. These variations are useful for evaluating how well algorithms capture non-linear geometry and handle incomplete manifolds in high-dimensional data. Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:scurve-tb-html)', '\\@ref(tab:scurve-tb-pdf)'))` summarizes these functions.

@@

To introduce missing or incomplete regions on the manifold, `gen_scurvehole(n, p)` (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:scurve) b"} else { "Figure \\@ref(fig:scurve-proj) b"})`) removes points in a localized region centered around the middle vertical section of the S-curve. Following a similar approach as `gen_cubehole(n, p, r_hole)`, all observations within a fixed radius ($\sqrt{0.3}$) of the anchor point are excluded, creating a hole in the manifold while preserving the overall S-curve structure.

### 2025-09-19 paper-cardinalR.tex
Updated pyramid section and added fixed radius value

An S-curve structure (Figure \ref{fig:scurve-proj}) simulates data that lies along a smooth, non-linear manifold. The functions generate both the standard S-curve shape and, similar to the cube generator, an S-curve variant with structured hole that introduce missing or incomplete region. These variations are useful for evaluating how well algorithms capture non-linear geometry and handle incomplete manifolds in high-dimensional data. Table \ref{tab:scurve-tb-pdf} summarizes these functions.

@@

To introduce missing or incomplete regions on the manifold, \texttt{gen\_scurvehole(n,\ p)} (Figure \ref{fig:scurve-proj} b) removes a subset of points near a designated anchor, creating a hole in the S-curve. This produces a hollowed manifold while preserving the overall curvature and structure of the S-curve.

>>>>

An S-curve structure (Figure \ref{fig:scurve-proj}) simulates data that lies along a smooth, non-linear manifold. The functions generate both the standard S-curve shape and, a S-curve variant with structured hole that introduce missing or incomplete region. These variations are useful for evaluating how well algorithms capture non-linear geometry and handle incomplete manifolds in high-dimensional data. Table \ref{tab:scurve-tb-pdf} summarizes these functions.

@@

To introduce missing or incomplete regions on the manifold, \texttt{gen\_scurvehole(n,\ p)} (Figure \ref{fig:scurve-proj} b) removes points in a localized region centered around the middle vertical section of the S-curve. Following a similar approach as \texttt{gen\_cubehole(n,\ p,\ r\_hole)}, all observations within a fixed radius (\(\sqrt{0.3}\)) of the anchor point are excluded, creating a hole in the manifold while preserving the overall S-curve structure.
